Instant Continuation Marks--Just Add $\lambda$

### 2012-10-15 proof.tex
Easier to follow.

\begin{lemma}[Simulation]
For all contexts $E\in\lambda_{cm}$ and expressions $e\in\lambda_{cm}$, $E[e]\cmrr E'[e']\implies\C{E[e]}\lvrrs\C{E'[e']}$
\end{lemma}

@@

\begin{corollary}
\label{cor:great}
For all contexts $E$ and terms $e\in\lambda_{cm}$, if $E[e]\cmrrs v$, then $\C{E[e]}\lvrrs\Cp{v}$.
\end{corollary}

\begin{proof}
%Let $E\in\lambda_{cm}$ and $e\in\lambda_{cm}$ be arbitrary.
By simulation.
\end{proof}

%\newtheorem{maintheorem}{Correctness of $\hat{\mathcal{C}}$}
\begin{theorem}
For all programs $p\in\lambda_{cm}$, $\Chcps{\mathrm{eval}_{cm}(p)}=\mathrm{eval}_{v}(\Chcps{p})$.
\end{theorem}

@@

\begin{align*}
p\cmrrs v &\implies\hole[p]\cmrrs v &\text{(since $p\cmrr\hole[p]$)}\\
          &\implies\C{\hole[p]}\lvrrs\Cp{v} &\text{(by corollary \ref{cor:great})}\\
          &\implies\app{\app{\app{\C{p}}{\C{\hole}}}{\xi(\hole)}}{\Cp{\chi(\hole)}}\lvrrs\C{v}&\text{by definition of $\mathcal{C}$}\\
          &\implies\Ch{p}\lvrrs\C{v}&\text{(by definition of $\hat{\mathcal{C}}$)}\\
          &\implies\mathrm{eval}_{v}(\Ch{p})=\Cp{v} &\text{(by definition of $\mathrm{eval}_v$)}
\end{align*}

>>>>

\begin{lemma}[Simulation]
For all contexts $E\in\lambda_{cm}$ and expressions $e\in\lambda_{cm}$, $E[e]\cmrr E'[e']\implies\Ccps{E[e]}\lvrrs\Ccps{E'[e']}$
\end{lemma}

@@

\begin{lemma}
\label{lem:great}
For all contexts $E$ and terms $e\in\lambda_{cm}$, if $E[e]\cmrrs v$, then $\Ccps{E[e]}\lvrrs\Cpcps{v}$.
\end{lemma}

\begin{proof}
%Let $E\in\lambda_{cm}$ and $e\in\lambda_{cm}$ be arbitrary.
If $E[e]\cmrrs v$, then $E[e]\cmrrs\hole[v]\cmrr v$.

By simulation, $E[e]\cmrrs\hole[v]\implies\Ccps{E[e]}\lvrrs\Ccps{\hole[v]}$.

By definition, $\Ccps{\hole[v]}=\app{\app{\app{\Ccps{v}}{\Ccps{\hole}}}{\xi(\hole)}}{\Cpcps{\chi(\hole)}}\lvrrs\Cpcps{v}$, which is what we sought.
\end{proof}

%\newtheorem{maintheorem}{Correctness of $\hat{\mathcal{C}}$}
\begin{theorem}[Correctness of $\mathcal{C}_{\mathrm{cps}}$]
For all programs $p\in\lambda_{cm}$, $\Chcps{\mathrm{eval}_{cm}(p)}\equiv\mathrm{eval}_{v}(\Chcps{p})$.
\end{theorem}

@@

\begin{align*}
p\cmrrs v &\implies\hole[p]\cmrrs v &\text{(since $p\cmrr\hole[p]$)}\\
          &\implies\C{\hole[p]}\lvrrs\Cp{v} &\text{(by lemma \ref{lem:great})}\\
          &\implies\app{\app{\app{\C{p}}{\C{\hole}}}{\xi(\hole)}}{\Cp{\chi(\hole)}}\lvrrs\C{v}&\text{by definition of $\mathcal{C}$}\\
          &\implies\Ch{p}\lvrrs\C{v}&\text{(by definition of $\hat{\mathcal{C}}$)}\\
          &\implies\mathrm{eval}_{v}(\Ch{p})=\Cp{v} &\text{(by definition of $\mathrm{eval}_v$)}
\end{align*}
